% test test test test test testtest test % testtest test testtest
% test testtest test testtest test testtest test testtest test test
% test test testtest test testtest test testtest test testtest
% test testtest test testtest test test test test testtest test
% testtest test testtest test testtest test testtest test testtest
% test testtest test testtest test testtest test testtest test
% testtest test testtest test testtest test testtest test testtest
% test testtest test testtest test testtest test testtest test
% testtest test test test test testtest test testtest test
% testtest test testtest test testtest test testtest test testtest
% test test

\begin{eqnarray*}
testf \equiv testf \mod testf
\end{eqnarray*}

\begin{eqnarray}
testg \equiv testg \mod testg
\end{eqnarray}

teat tfst tgst test
\begin{eqnarray*}
testf \equiv testf \mod testf
\end{eqnarray*}

Here is some more text with a formula $e=m\cdot c^2$ in between. This
will hopefully be caught, as well as our double dollar formula:
$$E=MC^2$$

The same can of course be done for formulas that are written in ghe
following way: \(F = \frac{m_1 \cdot m_2 \cdot G}{r^2}\)
Or, similar to the double dollar
\[F = a + n + g + d\]\\[12pt]

Another formula, right after
\[O=s^naps\]

\begin{itemize}
\item reperror
\item reperror
\item reperror
\item reperror
\item reperror
\item reperror
\end{itemize}

\section{another another another}

\setlength{35}

We need more words here. Hence, I am writing how I feel here. I feel
great. Life cannot be better. I hopefully will have functioning code
soon here, so that I can use it for my papers/my dissertation
etc. Just a few more words so that the 200 word trigger will be
executed.
I don't know why I am not doing less than the word-block size. I guess
my code is easier to manage in this way.

One of my best friends has birthday tomorrow. I should call him and
not forget it. I guess I will look into this test-file tomorrow and
see this message and it will make me not forget.

Furthermore, Halloween is coming up. I am looking forward to celebrate
this. I need to see if I can get a big cardboard box so that I can
pretend to be a garbage can and scare people walking by.
